Towards human SuperEEG

### 2018-10-06 paper/boneyard.tex

\section*{Introduction}
Current human brain recording techniques are fraught with compromise.
Commonly used approaches include functional magnetic resonance imaging
(fMRI), scalp electroencephalography (EEG), and magnetoencephalography
(MEG).  For each of these techniques, neuroscientists
and electrophysiologists must choose to optimize spatial resolution
at the cost of temporal resolution (e.g.\ as in fMRI) or temporal
resolution at the cost of spatial resolution (e.g.\ as in EEG
and MEG).  A less widely used approach (due to requiring work with
neurosurgical patients) is to record from electrodes implanted
directly onto the cortical surface (electrocorticography; ECoG) or
into deep brain structures (intracranial EEG; iEEG).  However, these
intracranial approaches also require compromise: the high temporal and
spatial resolutions of intracranial recordings comes at the cost of
substantially reduced brain coverage, since safety considerations
limit the number of electrodes one may implant in a given patient's
brain.  Further, the locations of implanted electrodes are determined by clinical,
rather than research, needs.

>>>>

\section*{Introduction}
% JRM thoughts:
% - Tie in stats from supplemental analyses.  Fig S4: total number of
% electrodes, total number of used electrodes, prop thresholded, total
% recording time, average session time, number of sessions.

(i.e.,
relying on a combination of volume conductance

(Across shown in black, see Fig.~\ref{fig:corrmap}A). We also
reconstructed activity for each electrode using a model trained on the
remaining electrodes from only that patient, to account for
reconstruction accuracy attributed to volume conductance alone (Within
shown in gray, see Fig.~\ref{fig:corrmap}A). For the first dataset, we
compared these two distributions of correlation coefficients (paired
$t$-test between $z$-transformed mean correlation coefficients by
patient: $t(66) = 9.64, p < 10\textsuperscript{-10}$).  We repeated
this analysis on a similar dataset Fig.~\ref{fig:corrmap}C) with
similar results (paired $t$-test between $z$-transformed mean
correlation coefficients by patient:
$t(23) = 6.93, p < 10\textsuperscript{-5}$). This is an especially
conservative test, given that the SuperEEG reconstructions exclude
(from the correlation matrix estimates) all data from the patient
whose data is being reconstructed.  Furthermore, we also replicated
this finding for each independent experiment within dataset 2 (Fig. S3
(paired $t$-test between $z$-transformed mean correlation coefficients
by patient for experiment 1:
$t(23) = 6.23, p < 10\textsuperscript{-5}$ and experiment 2:
$t(23) = 6.62, p < 10\textsuperscript{-5}$).

%%%

Current human brain recording techniques are fraught with compromise.
Commonly used approaches include functional magnetic resonance imaging
(fMRI), scalp electroencephalography (EEG), and magnetoencephalography
(MEG).  For each of these techniques, neuroscientists
and electrophysiologists must choose to optimize spatial resolution
at the cost of temporal resolution (e.g.\ as in fMRI) or temporal
resolution at the cost of spatial resolution (e.g.\ as in EEG
and MEG).  A less widely used approach (due to requiring work with
neurosurgical patients) is to record from electrodes implanted
directly onto the cortical surface (electrocorticography; ECoG) or
into deep brain structures (intracranial EEG; iEEG).  However, these
intracranial approaches also require compromise: the high temporal and
spatial resolutions of intracranial recordings comes at the cost of
substantially reduced brain coverage, since safety considerations
limit the number of electrodes one may implant in a given patient's
brain.  Further, the locations of implanted electrodes are determined by clinical,
rather than research, needs.
